A fast primal-dual algorithm for computing Nash equilibria and best response strategies in two-person zero-sum sequential games

### 2014-08-13 paper.tex
refactor

\begin{remark}
  In practice, $A$, $E$, and $F$ are very sparse: $A$ will be sparse because a concrete sequential game will
typically have very few\footnote{Few, relative to the size of the game tree.} leafs, and only a few
combinations of sequences of moves of the players, will actually lead to a leaf (i.e. end the game);
$E$ and $F$ will be sparse because the kinks of possible sequences of moves of each player will
zig-zag between only a limited number of the player's information sets so that a move at an information set will
rarely\footnote{Relative to the number of information sets for the player.}  extend another information set.
This sparsity should be thoroughly exploited\footnote{For example when
multiplying vectors with these matrices.} by a solver for problem \eqref{eq:opt_pb}.
\end{remark}

@@

\section{The proposed algorithm}
0\label{sec:algo}
In this section we present the algorithm which is the purpose of this paper, namely an algorithm
for solving \eqref{eq:opt_pb}. Our algorithm (Alg.\ref{Tab:algo}) is a use-case of
the generic primal-dual algorithm of A. Chambolle and T. Pock, namely Algorithm 1 of \cite{chambolle2010}.

>>>>

\begin{remark}
  In practice, $A$, $E$, and $F$ are very sparse.
%% : $A$ will be sparse because a concrete sequential game will
%% typically have very few\footnote{Few, relative to the size of the game tree.} leafs, and only a few
%% combinations of sequences of moves of the players, will actually lead to a leaf (i.e. end the game);
%% $E$ and $F$ will be sparse because the kinks of possible sequences of moves of each player will
%% zig-zag between only a limited number of the player's information sets so that a move at an information set will
%% rarely\footnote{Relative to the number of information sets for the player.}  extend another information set.
This sparsity should be thoroughly exploited\footnote{For example when
multiplying vectors with these matrices.} by a solver for problem \eqref{eq:opt_pb}.
\end{remark}

@@

\section{The proposed algorithm}
\label{sec:algo}
In this section we present the algorithm which is the purpose of this paper, namely an algorithm
for solving \eqref{eq:opt_pb}. Our algorithm (Alg.\ref{Tab:algo}) is a use-case of
the generic primal-dual algorithm of A. Chambolle and T. Pock, namely Algorithm 1 of \cite{chambolle2010}.
